Open Data, Open Source and Open Standards in chemistry: \\ The Blue Obelisk five years on

### 2011-06-13 paper.tex
Fix typo reported by Kevin Thiesen

At the time of writing there are many commercial companies development chemistry
solutions around Open Source cheminformatics components provided by the Blue Obelisk
community. Examples of such companies include iChemLabs, IdeaConsult, Wingu, Silicos,
GenettaSoft, eMolecules, hBar, Metamolecular, and Inkspot Science. Some of these merely use components, but several
actively contribute back to the Blue Obelisk project they use, or donate new
Open Source cheminformatics projects to the community.

>>>>

At the time of writing there are many commercial companies developing chemistry
solutions around Open Source cheminformatics components provided by the Blue Obelisk
community. Examples of such companies include iChemLabs, IdeaConsult, Wingu, Silicos,
GenettaSoft, eMolecules, hBar, Metamolecular, and Inkspot Science. Some of these merely use components, but several
actively contribute back to the Blue Obelisk project they use, or donate new
Open Source cheminformatics projects to the community.
